---
title: "Ryan Tillis - Interactive Data Mapping - Data Products - Coursera"
author: <a href="http://www.ryantillis.com"> Ryan Tillis </a>
date: "6/28/2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Interactive Map Assignment: Developing Data Products

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

##Submission

By accessing the Open Data NYC api we can look at art museum locations in New York City.


```{r cars}
library(jsonlite)
library(leaflet)
data <- fromJSON("https://data.cityofnewyork.us/resource/43hw-uvdj.json", flatten = TRUE)

artLatLong <- data.frame(
  lat = unlist(lapply(data$the_geom.coordinates, `[[`, 2)),
  lng = unlist(lapply(data$the_geom.coordinates, `[[`, 1))
)

artIcons <- makeIcon(
  iconUrl = "https://people.ucsc.edu/~admcnich/images/pin.svg",
  iconWidth = 35*215/230, iconHeight = 35,
  iconAnchorX = 35*215/230/2, iconAnchorY = 35
)

artSites <- paste("<a href='", data$url, "'>",data$name,"</a>" ,sep = "")

artLatLong %>% leaflet() %>% addTiles() %>%
addMarkers(icon=artIcons, popup = artSites)
```

<hr>

See more at <a href="http://www.ryantillis.com"> my website. </a>

<hr>
